Manuscript plots

### 2024-04-26 manuscript_modelling_and_plots.Rmd
figs with new x axis labels, experiment materials, and associated code for figs

@@

# relationship between the effect of N-back and age
age.nback.effect.sge <- ggplot(ageranef, aes(age.c, ranef.age.pred.tot)) + 
  geom_vline(xintercept = 0, size = .5, color = "black", linetype="solid") +
  geom_hline(yintercept = mean(ranef.age.pred.tot), size = .5, color = "black", linetype="solid") +
  geom_jitter(height = 0, width = 0, size = 4,
              shape = 21, colour = "black", fill = viridis(5)[3], alpha = .95, stroke = 1) + 
  stat_smooth(method = 'lm', ci = T, color = viridis(5)[3], size = 1) + 
  xlab("Age (mean centered)") +
  ylab(expression("Individual effects of N-back on"~ H[s])) +
  #ylim(-.15, .1) +
  theme_bw() +
  theme(legend.position = "bottom", legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 15), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 15), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), strip.text = element_text(face = "bold", size = 10))

@@

@@

#
age.nback.effect.gte <- ggplot(ageranef, aes(age.c, ranef.age.pred.tot)) + 
  geom_vline(xintercept = 0, size = .5, color = "black", linetype="solid") +
  geom_hline(yintercept = mean(ranef.age.pred.tot), size = .5, color = "black", linetype="solid") +
  stat_smooth(method = 'lm', ci = T, color = viridis(5)[3], size = 1) + 
  geom_jitter(height = 0, width = 0, size = 4,
              shape = 21, colour = "black", fill = viridis(5)[3], alpha = .95, stroke = 1) + 
  xlab("Age (mean centered)") +
  ylab(expression("Individual effects of N-back on"~ H[t])) +
  #ylim(-.15, .1) +
  theme_bw() +
  theme(legend.position = "bottom", legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 15), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 15), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), strip.text = element_text(face = "bold", size = 10))

>>>>

# load model
sge.fit.4 <- readRDS(here::here("gaze_entropy_heterogenous/models/sge_fit_4.rds"))

@@

# relationship between the effect of N-back and age
age.nback.effect.sge <- ggplot(ageranef, aes(age.c, ranef.age.pred.tot)) + 
  geom_vline(xintercept = 0, size = .5, color = "black", linetype="solid") +
  geom_hline(yintercept = mean(ranef.age.pred.tot), size = .5, color = "black", linetype="solid") +
  geom_jitter(height = 0, width = 0, size = 4,
              shape = 21, colour = "black", fill = viridis(5)[3], alpha = .95, stroke = 1) + 
  stat_smooth(method = 'lm', ci = T, color = viridis(5)[3], size = 1) + 
  xlab("Age (mean centered)") +
  ylab(expression("Implied total heterogeneity of "~ H[s])) +
  #ylim(-.15, .1) +
  theme_bw() +
  theme(legend.position = "bottom", legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 15), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 15), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), strip.text = element_text(face = "bold", size = 10))

@@

# load model
gte.fit.7 <- readRDS(here::here("gaze_entropy_heterogenous/models/gte_fit_7.rds"))

@@

#
age.nback.effect.gte <- ggplot(ageranef, aes(age.c, ranef.age.pred.tot)) + 
  geom_vline(xintercept = 0, size = .5, color = "black", linetype="solid") +
  geom_hline(yintercept = mean(ranef.age.pred.tot), size = .5, color = "black", linetype="solid") +
  stat_smooth(method = 'lm', ci = T, color = viridis(5)[3], size = 1) + 
  geom_jitter(height = 0, width = 0, size = 4,
              shape = 21, colour = "black", fill = viridis(5)[3], alpha = .95, stroke = 1) + 
  xlab("Age (mean centered)") +
  ylab(expression("Implied total heterogeneity of "~ H[t])) +
  #ylim(-.15, .1) +
  theme_bw() +
  theme(legend.position = "bottom", legend.direction = "horizontal", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 15), axis.title.y = element_text(size = 11), axis.text.y = element_text(size = 15), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), strip.text = element_text(face = "bold", size = 10))
